%-------------------------
% Resume in Latex
% Author : Chandra Prakash Dixit
% Based off of: https://github.com//resume
% License : MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage{charter}
\usepackage{fontawesome5} % for icons e.g. mail, mobile, linkedin, github etc


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      %\small#3 & \small #4 \
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     %\textit{\small#1} & \textit{\small #2} \\
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Chandra Prakash Dixit} \\ \vspace{2pt}
    \faIcon{map-marker-alt}  \small Bengaluru, KA, IN 
    $|$ \faIcon{mobile-alt} +91-9452-100-509 
    $|$ \faIcon{envelope} \href{mailto:dixitchandra.cpp@gmail.com}{\underline{dixitchandra.cpp@gmail.com}} 
    $|$ \faIcon{linkedin-in} \href{https://www.linkedin.com/in/dixit-chandra/}{\underline{dixit-chandra}}
%    $|$ \faIcon{github} \href{https://github.com/littledroplets}{\underline{littledroplets}} 
%    $|$ \faIcon{link} \href{https://littledroplets.github.io/}{\underline{Website}}
\end{center}


%-----------PROFILE-----------

\section{Profile}
\resumeSubHeadingListStart
		{\item
		{Experienced C++ Developer, well versed with concepts of Object Oriented Programming, Data Structures \& Algorithms; adept in bringing forth expertise in design, development, testing and maintenance of cross-platform software systems. Equipped with a diverse and promising skill-set. Familiar with the latest cutting-edge development tools, procedures \& methodologies; able to effectively self-manage during independent projects, as well as collaborate effectively within a productive team.}
		}
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
    \small{\item{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
     \textbf{Languages}{: C++ 11/14/17, Perl, Python, Lua} &
     \textbf{Frameworks}{: Google Test, Google protobuf, Qt} \\
     \textbf{Developer Tools}{: Git, VS Code, XCode, Qt Creator, Jenkins, Jira} &
     \textbf{Libraries}{: STL, boost, SOL} \\
     \end{tabular*}\vspace{-5pt}
    }}
 \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {{Master of Technology $|$ \emph{\small{Advanced Computing}}}}{Aug. 2016 -- Sep 2018}
      {Maulana Azad National Institute of Technology}{Bhopal, MP, IN}
    \resumeSubheading
      {{Bachelor of Technology $|$ \emph{\small{Computer Science \& Engineering}}}}{Jul. 2011 -- June 2015}
      {Dr. A.P.J. Abdul Kalam Technical University (formerly U.P.T.U.)}{Lucknow, UP, IN}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Developer}{March 2023 -- Present}
      {Broadridge Trading and Connectivity Solutions}{Bengaluru, KA, IN}
      \resumeItemListStart
        \resumeItem{Product: TBricks, an automated trading platform.}
        \resumeItem{Refactored existing code to improve readability and maintainability, resulting in a reduction in development time.}
        \resumeItem{Implemented new features and fixed existing issues resulting in improved user experience while learning about trading domain.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer}{Sep. 2022 -- Feb. 2023}
      {WorkFusion}{Hyderabad, TS, IN}
      \resumeItemListStart
        \resumeItem{Product: WorkFusion RPA, Control Tower.}
        \resumeItem{Responsible for code improvement, feature implementation and bug fixes for core RPA product while collaborating with team in Poland.}
        \resumeItem{Removed over 1200 memory leaks in code which resulted in drop in customer issues by more than 50\%.}
    \resumeItemListEnd
    
    \resumeSubheading
          {Consultant C++ Developer}{Dec. 2021 -- Sep. 2022}
          {MTX Group Inc.}{Hyderabad, TS, IN}
          \resumeItemListStart
            \resumeItem{Product: CI Tools by Central Innovations.}
            \resumeItem{Responsible for well documented, peer reviewed Add- on development \& maintenance for Windows \& Mac Platform of ArchiCAD software using SDK.}
            \resumeItem{Migrated complete set of CI tools to be compatible with ArchiCAD 26 in 30\% lesser time than  usual.}
        \resumeItemListEnd

    \resumeSubheading
      {Senior Engineer}{Jan. 2018 -- Dec. 2021}
      {John Deere}{Pune, MH, IN}
      \resumeItemListStart
        \resumeItem{Product: Gen4 Display for Precision Agriculture.}
        \resumeItem{Started as Intern, later converted to PGET and Promoted to Senior Engineer within as result of consistent performance.}
        \resumeItem{Responsible for implementation of business requirements coming from Product Owner and stakeholders for Gen4 Displays based on Wind River RTOS in Linux dev environment.}
        \resumeItem{Developed various applications for Gen4 Displays of various machines and implements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
      	{\textbf{TBRICKS Core Development}}{\emph{Broadridge}}
      		\resumeSubHeadingListStart
      			{\item
          			{Working as individual contributor in CORE back-end Team of automated trading platform, TBricks. I have worked on multiple back-end utilities while incorporating new features  \& providing bug fixes to various tbricks admin tools.
         			}
          		}
        	\resumeSubHeadingListEnd
       \resumeProjectHeading
       	{\textbf{RPA MFW}}{\emph{WorkFusion}}
       		\resumeSubHeadingListStart
       			{\item
       				{Worked on improving CORE DLL component of Workfusion RPA, A UI Manipulation framework written mainly with C++ and WIN32 API to simulate UI operations needed for RPA bots.}
             	}
	        \resumeSubHeadingListEnd
       \resumeProjectHeading
       	{\textbf{CI Tools - ArchiCAD Addon}}{\emph{MTX Group Inc}}
       		\resumeSubHeadingListStart
       			{\item
       				{Improved and migrated CI Tools Windows \& Mac add-on for ArchiCAD software through integrating new features \& fixing existing defects using ArchiCAD SDK.}
             	}
	        \resumeSubHeadingListEnd	        

       \resumeProjectHeading
       	{\textbf{Configurable Doc UI}}{\emph{John Deere}}
       		\resumeSubHeadingListStart
       			{\item
       				{Technical PoC Project at John Deere for Rapid deployment of updates instead of yearly release model; also added support of importing encrypted config files via USB and Cloud deployment.}
             	}
	        \resumeSubHeadingListEnd
       \resumeProjectHeading
       	{\textbf{Work Notes}}{\emph{John Deere}}
       		\resumeSubHeadingListStart
       			{\item
       				{Performed End to end execution of this feature which provides Machine operators with a framework to log Work-based observations \& export those to the cloud.}
             	}
	        \resumeSubHeadingListEnd
		\resumeProjectHeading
       	 {\textbf{Machine \& Work Monitor}}{\emph{John Deere}}
       		\resumeSubHeadingListStart
       			{\item
       				{Supporting multiple platforms over multiple releases for displaying \& logging various machine and work-related data coming from CAN Bus or other applications.}
             	}
	        \resumeSubHeadingListEnd
       \resumeProjectHeading
       	{\textbf{Social Media Analysis on YouTube Channel}}{\emph{John Deere}}
       		\resumeSubHeadingListStart
       			{\item
       				{Captured Customer emotions / needs from posted comments on John Deere India YouTube Channel. Analyzed comments and came-up with a solution to enable stakeholders to identify topics and sentiments to have more focused Action Items.}
             	}
	        \resumeSubHeadingListEnd	
       \resumeProjectHeading
       	{\textbf{Location driven Soil Analysis}}{\emph{John Deere}}
       		\resumeSubHeadingListStart
       			{\item
       				{Completed during Internship, in which I performed end-to-end project delivery including processing and analysis of publicly available soil data to create APIs to get soil property on basis of geographical location using QGIS.}
             	}
	        \resumeSubHeadingListEnd	                
%---------------Add New Project in future-------------------
%       \resumeProjectHeading
%       	{\textbf{Project-Name}}{\emph{Company-name}}
%       		\resumeSubHeadingListStart
%       			{\item
%       				{Work done / description of project, roles and responsibilities, impact}
%             	}
%	        \resumeSubHeadingListEnd	        	        
	\resumeSubHeadingListEnd




%-------------------------------------------
\end{document}
